---
title: "Lesson 12 - Hiding stuff"
author: "Eike"
date: "11/10/2021"
output: html_document
---

```{r, message=FALSE, include=FALSE}
require(chillR)
require(ggplot2)
Temperatures <- read.csv("data/Temperatures.csv")
```

```{r temperature_generation, message=FALSE, warning=FALSE, eval=FALSE}
require(chillR)
require(ggplot2)
Temp<-temperature_generation(KA_weather,
                             years=c(1998,2005),
                             sim_years = c(2001,2025))
Temperatures<-cbind(KA_weather[
  which(KA_weather$Year %in% 1998:2005),] ,Data_source="observed")
generated_temps<-cbind(Temp[[1]][,c("Year","Month","Day","Tmin","Tmax")],
                       Data_source="simulated")
Temperatures<-rbind(Temperatures,generated_temps)
```



```{r, fig.cap="Generated vs. simulated temperatures", message=FALSE}
Temperatures[,"Date"]<-as.Date(ISOdate(2000,
                                       Temperatures$Month,
                                       Temperatures$Day))

g <- ggplot(data=Temperatures, aes(Date,Tmax)) +
  facet_wrap(vars(Data_source)) +
  geom_smooth(aes(colour = factor(Year))) +
  theme(legend.position = "none") +
  scale_x_date(date_labels = "%b")
g

```




We'll try a few chunk options now:

* include = FALSE prevents code and results from appearing in the finished file. R Markdown still runs the code in the chunk, and the results can be used by other chunks.
* echo = FALSE prevents code, but not the results from appearing in the finished file. This is a useful way to embed figures.
* message = FALSE prevents messages that are generated by code from appearing in the finished file.
* warning = FALSE prevents warnings that are generated by code from appearing in the finished.
* eval = FALSE prevents code from being evaluated.
* fig.cap = "..." adds a caption to graphical results.

